---
title: "interpretation_of_results"
author: "Alejandro Pineda"
format: html
editor: visual
---

## Interpretation of results

The first step is storing the csv file

```{r}
#install.packages("readr")
#install.packages("ggplot2")
#install.packages("dplyr")
library("readr")
library("ggplot2")
library("dplyr")
```

```{r}
DF <- read_csv("results/results_1.csv")
DF
```

For each prompting technique, we'll see its histogram

```{r}

for (i in 1:5) {
  nombre_fila <- DF[i, 1] 
  
  datos_fila <- as.numeric(DF[i, -1]) 
  
  hist(datos_fila,
       breaks = seq(0, 1, by = 0.05),
       xlim = c(0, 1),
       ylim = c(0, 50),
       col = "steelblue",
       main = nombre_fila,
       xlab = "",
       ylab = "Frecuency")
  
mtext("Values (Escale from 0 to 1)", side = 1, line = 2.3, cex = 0.9)
  
mtext(paste("Average score:", mean(datos_fila)), side = 1, line = 3.3, cex = 0.9, font = 2, col = "darkblue")
  
mtext(paste("Least value", min(datos_fila)), side = 1, line = 4.3, cex = 0.9, font = 2, col = "darkgreen")
  
}


```

All the histograms have a tendency to the right, showing that all of them achieved good scores. In addition, the minimum value secured by each technique is greater than 0.6.

However, despite the good results obtained by Skeleton-of-thought and Template pattern, the graphics show that the techniques that stand out are Persona Pattern, Refining Prompt, and Zero-shot Baseline.\
This affirmation is based on the histograms, were the latter showed more consistence, having scores greater than 0.9 in most of the textbooks' chapters.\
\
Having all the performances, it's precise to verify the initial hypothesis and try to find a specific technique that works best.

Following the methods described before, and using the next script:

```{r}
df <- DF
prompts <- df$prompt

# Remove the prompt column so only scores remain
scores <- as.matrix(df[, -1])

n <- length(prompts)

# Pairwise wins matrix
wins <- matrix(0, nrow = n, ncol = n,
               dimnames = list(prompts, prompts))

# Number of pairwise victories
victories <- setNames(rep(0, n), prompts)

for (i in 1:(n-1)) {
  for (j in (i+1):n) {

    i_votes <- sum(scores[i, ] > scores[j, ])
    j_votes <- sum(scores[j, ] > scores[i, ])

    wins[i, j] <- i_votes
    wins[j, i] <- j_votes

    if (i_votes > j_votes) {
      victories[i] <- victories[i] + 1
    } else if (j_votes > i_votes) {
      victories[j] <- victories[j] + 1
    }
  }
}

print(wins)
print(victories)

# Condorcet winner
winner <- names(victories[victories == n - 1])

if (length(winner) == 0) {
  cat("No Condorcet winner.\n")
} else {
  cat("Condorcet winner:", winner, "\n")
}
```

Condorcet method shows that Refining Prompt is the strategy that performed well in most of the cases.

On the other hand, the Refining Prompt was also the technique with the highest average.

Both of results agree, so we can conclude the Refining Prompt is the technique that works best in most of the cases.
